Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2020-01-17 paper/manuscript.tex
minor change

Many of the issues around simualtion setup and protocol choice for alchemical calculations are common, but there are some differences between absolute and relative calculations. First we will consider protocol differences  so before treating the common elements.

>>>>

Many of the issues around simulation setup and protocol choice for alchemical calculations are common, but there are some differences between absolute and relative calculations. First we will consider protocol differences  so before treating the common elements.
